Water Management

### 2020-02-20 Paper/paper.tex
add subsection evaporation

\clearpage	
\newpage
\printbibliography

>>>>

\clearpage	
\newpage

\subsection{Evaporation}
In the following, we want to assess the effect of evaporation on the optimal irrigation policy and the steady state. 
As described in \ref{intro-mod4}, we derive the amount of evaporation over time from other weather related and geographical data. 
The (calculated) evaporation has a low volatility over the years and has value of approximately 1 unit, as \ref{fig:without-vs-with-evaporation} shows. 
Due to the fact that the reservoir has a fixed capacity of 7 units, rainfall that would fill the reservoir above this value is not available for further use. 
When taking evaporation into account, the reservoir never reaches its capacity limits and thus all rainfall will be saved. This leads to an increased volatility of the water level. 
\\

\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-inactive.eps}
	\caption{Without Evaporation}
	\label{fig:rainfall-real-data}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[width=1\textwidth]{figures/results-opt-irrigation-over-time-evap-active.eps}
	\caption{With Evaporation}
	\label{fig:value-function}
\end{subfigure}
\caption{Comparison of water level, irrigation amount, rainfall and evaporation over time using real data}
\label{fig:without-vs-with-evaporation}
\end{figure}

As expected, the average water level is lower with evaporation than without, which in return leads to a lower irrigation the farmers are allowed to receive. \\
We should not at this point, that under the assumptions made, this simulation does not allow for evaporation effects that outweigh the rainfalls, as this would dry out the reservoir. The reason for this limit is found in the utility functions of the farmers and the recreational users. Because of $x\leq s$, we get for $s\to 0 \Rightarrow x\to 0$, and as a consequence

\begin{equation}
\lim_{s, x\to0}F(x) = \lim_{s,x\to0}-\frac{1}{x} = -\inf
\end{equation}

as well as

\begin{equation}
\lim_{s, x\to0}G(s,x) = \lim_{s,x\to0}-\frac{1}{(s-x)^2} = -\inf
\end{equation}

%TODO den folgenden Absatz rauswerfen?
How then can these utility functions be interpreted in terms of reality? 
An utility value of negative infinity may be reasonable, if an actor has no alternative actions available. 
In this scenario, we could imagine this to be an isolated village, where the only possibility for the farmers to irrigate their fields is to use water from this particular reservoir, and the only way to have food for survive is to make use of their own fields (nothing else to do, no trading for example), assuming that the farmers want to survive.

\printbibliography
